---
title: "Chapter 5 Practice"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Hack-A-Prompt

## Prompt draft

Persona: Act as a R programmer.
Task: Help me write a block of R code meeting these specifications: 

- define a `sales_q1` collection with the values 120, 135, 150, and 160

- define a `sales_q2` collection with the values 125, 130, 155, and 170

- define `growth` by taking the difference between `sales_q2` and `sales_q1`

- define `positive_growth` by taking all positive values from `growth`

- define `last_two` as the final two values in `sales_q2`

- output the length of `sales_q1` and `sales_q2`

- output the class of `growth`

## LLM output

```{r LLM output}
# Define sales collections
sales_q1 <- c(120, 135, 150, 160)
sales_q2 <- c(125, 130, 155, 170)

# Calculate growth (difference between Q2 and Q1)
growth <- sales_q2 - sales_q1

# Extract positive growth values
positive_growth <- growth[growth > 0]

# Get the last two values from sales_q2
last_two <- tail(sales_q2, 2)

# Output the length of both sales collections
cat("Length of sales_q1:", length(sales_q1), "\n")
cat("Length of sales_q2:", length(sales_q2), "\n")

# Output the class of growth
cat("Class of growth:", class(growth), "\n")
```
## Output vs target

I used the *boisestate.ai* LLM and the result matched exactly when defining `sales_q1`, `sales_q2`, and `positive_growth`, but it differed on defining `last_two` and it added additional text to the result for the two length outputs and the class output.

I actually like the way it approached defining `last_two` because it is more dynamic if the length of `sales_q2` were to change, but I will have to specify that I only want the values in the third and fourth position in order to get the code to match exactly. 

I will also specify that I only want to print the resulting length values and the class.

## Prompt - revised

Persona: Act as a R programmer.
Task: Help me write a block of R code meeting these specifications: 

- define a `sales_q1` collection with the values 120, 135, 150, and 160

- define a `sales_q2` collection with the values 125, 130, 155, and 170

- define `growth` by taking the difference between `sales_q2` and `sales_q1`

- define `positive_growth` by taking all positive values from `growth`

- define `last_two` as the third and fourth value in `sales_q2`

- output the value of the length of `sales_q1` and `sales_q2`

- output the name of the class of `growth`

## LLM output - revised

```{r LLM output - revised}
# Define sales collections
sales_q1 <- c(120, 135, 150, 160)
sales_q2 <- c(125, 130, 155, 170)

# Calculate growth (difference between Q2 and Q1)
growth <- sales_q2 - sales_q1

# Extract positive growth values
positive_growth <- growth[growth > 0]

# Get the third and fourth values from sales_q2
last_two <- sales_q2[3:4]

# Output the length values
length(sales_q1)
length(sales_q2)

# Output the class name
class(growth)
```

## Output vs target - revised

I used the same LLM thread and provided the revised prompt. The result is closer to the goal, with one small difference. The LLM result used sales_q2[3:4] instead of sales_q2[c(3,4)] to define `last_two`. This is a very minimal difference as the resulting vector will be the same in both cases.