---
title: "Chapter 6 Practice"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

## Task 1: Help-file scavenger hunt

```{r}
?sample
```

Looking at the **Usage** line, I can tell that `x` and `size` are required because they *do not* have an `=` sign. `replace` and `prop` are default because they *do* have an `=` sign.

Usage

sample(x, size, replace = FALSE, prob = NULL)

sample.int(n, size = n, replace = FALSE, prob = NULL,
           useHash = (n > 1e+07 && !replace && is.null(prob) && size <= n/2))

Required arguments:

- x

- size

Default arguments:

- replace = FALSE

- prob = NULL

## Task 2: Build a random data set

```{r}
set.seed(1)

pool <- seq(from = 60, to = 100)
scores_numbers <- sample(pool, 25, replace = TRUE)
scores <- c(scores_numbers, NA, NA, NA)

length(scores)
```

Initialized the seed to be 1 so that all tests are the same.

First, used the from and to arguments in seq() to define pool. Then, used sample() and provided pool as the vector from which to choose, 25 for the number of elements to choose from, and specified that I want replacement. Finally, added an additional 3 `NA` values to the end to create a vector of length 28.

## Task 3: Handle missing data

```{r}
n_missing <- sum(is.na(scores))
n_missing

average_raw <- mean(scores)
average_raw

average_scores <- mean(scores, na.rm = TRUE)
average_scores
```
`average_raw` is NA because the default argument for na.rm is FALSE, meaning that NA values are included in the mean calculation. By removing NA values, `average_scores` is the mean of all values remaining.

## Task 4: Locate missing values

```{r}
scores_is_missing <- is.na(scores)

missing_positions <- which(is.na(scores_is_missing))

print(scores_is_missing)
print(missing_positions)
length(missing_positions)
```

Whoops, in order to use which(is.na()), I need to use `scores`, not `scores_is_missing`. Alternatively I could have used `which(scores_is_missing)`.

```{r}
scores_is_missing <- is.na(scores)

missing_positions <- which(is.na(scores))

print(scores_is_missing)
print(missing_positions)
length(missing_positions)
```

This result is telling me that the NA values are in positions 26-28 in `scores`, and that the total number of NA values is 3.

## Task 5: Nesting functions

```{r}
set.seed(21)
mean_of_five <- mean(sample(scores, 5), na.rm = TRUE)

mean_of_five
```

I nested sample inside of mean, and chose to not use replacement (defaulted to FALSE). To make sure NA is removed if selected in the sample, I used na.rm = TRUE.

## Task 6: Quick time-stamp

```{r}
today_date <- Sys.Date()
today_time <- Sys.time()
```

I like to use this to append on processed files' filenames - so helpful!

## Task 7: Handling missing values

```{r}
scores_clean <- scores[!is.na(scores)]

length(scores)
length(scores_clean)
```

By using `!`, I am essentially saying that `scores_clean` is all values in the `scores` vector except for any that are NA (or in other words, keep everything that is *not* NA).

```{r}
scores_imputed <- scores

scores_imputed[is.na(scores_imputed)] <- mean(scores_imputed, na.rm = TRUE)

# checks
sum(is.na(scores_imputed))
mean(scores_imputed)
print(scores_imputed[26:28])
```

This worked as expected, and since we already found out that positions 26-28 were NA in `scores`, printed the scores_imputed values in those positions to verify that they are indeed the same as the mean. Neat-o.

## Task 8: Reflection

A function object is the function itself whereas a function call is when the function is executed. The function call will always have parentheses where arguments may be passed into the function, if needed.