---
title: "Chapter 3 Practice"
output: html_notebook
---

Goal: Practice creating vectors and doing arithmetic
Verify: I should see three outputs: x+y, x*2, and x/y

```{r 2.5 Run Code Chunks}
x <- c(2, 4, 6)
y <- c(1, 3, 5)

x + y
x * 2
x / y
```
```{r 3.0.1 Recycling Vecotrs}
numbers3 <- c(1.5, 2.5, -3.5)
combination <- c(1, 2, 3, 4, 5)
recycled_result <- numbers3 + combination

print(recycled_result)

long <- c(6, 2, 8, 10, 3, 77)
short <- c(88, 4, 20)
difference <- long - short

print(difference)
```
Memo: R recycles the shorter vector when adding and subtracting. A warning appears when the longer length is not a multiple of the shorter length, but this does not create a hard-stop error.

```{r 5.1 Class and Behavior}
today <- as.Date("2026-01-20")
mode(today)
class(today)

today + 7
```
```{r 5.3 Character strings}
first_word <- "yellow"
second_word <- "banana"

sentence <- paste(first_word,second_word)
sentence

class(sentence)

first_names <- c("Demi", "Snoop", "Ed")
last_names <- c("Moore", "Dogg", "Sheeran")
full_names <- paste(first_names, last_names)
full_names

```
Memo: I wasn't expecting a space between the two words pasted together, but now I see that paste0 eliminates that space.

```{r 5.4.1 Creating Factors}
grades <- c("A", "B", "C", "A", "B", "A")
grades <- factor(grades)

mode(grades)
class(grades)
print(grades)
```
```{r 5.4.2 Levels and Ordering}
sizes <- c("Medium", "Large", "Small", "Medium", "Large")
sizes <- factor(sizes, levels = c("Small", "Medium", "Large"))

print(sizes)
```
```{r 5.4.3 Data Coercion}
mixed <- c("candy", 4, "book", 92)
class(mixed)

as.numeric(c("1", "2", "3"))
as.numeric(mixed)
```

```{r 5.5 Named Vectors}
nerdy_palette <- c("Octarine" = "#7F00FF", "TARDIS Blue" = "#003B6F",
                   "Rebeccapurple" = "#663399", "Hooloovoo" = "#4F97A3")
print(nerdy_palette)
names(nerdy_palette)

nerdy_palette["Octarine"]

nerdy_palette[c("Octarine", "TARDIS Blue", "NotAColor")]

nerdy_palette[c(1,3)]
```
Memo: Looks like indexing starts at 1, not zero

```{r 6 Logical Vectors}
real <- c(FALSE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, TRUE, NA)
print(real)

logicals <- c(1 > 2, 3 < 5, 4 == 4)
print(logicals)
```
```{r 7 Lists}
taylor_swift_list <- list(
  name = "Taylor Swift",
  albums = c("Fearless", "Red", "1989", "folklore", "Midnights"),
  release_years = c(2008, 2012, 2014, 2020, 2022),
  album_of_the_year_wins = c(TRUE, FALSE, TRUE, TRUE, FALSE),
  favorite_song = list(
    title = "All Too Well (10 Minute Version)",
    album = "Red",
    length_minutes = 10.13
  ) 
)

print(taylor_swift_list)
```
# Practice Space
### 10.1 Task 1
Building numeric vectors
```{r 10.1 Task 1}
sales_q1 <- c(5, 10, 15, 20)
sales_q2 <- c(1, 2, 3, 4)

print(sales_q1)
print(sales_q2)

length(sales_q1)
length(sales_q2)

```
The output shows two vectors, both with a length of 4.

### 10.2 Task 2
Vector arithmetic
```{r 10.2 Task 2}
growth <- sales_q2 - sales_q1
growth
```
The output shows a decrease in sales from Q1 to Q2.

### 10.3 Task 3
Exponents and vectorized math
```{r 10.3 Task 3}
exponents <- c(0:10)
binary_powers <- 2 ^ exponents

length(binary_powers)
```
The output shows 11 elements (values) in the `binary_powers` vector.

### 10.4 Task 4
Element-wise subtraction
```{r 10.4 Task 4}
cursed_seq <- c(4L, 8L, 15L, 16L, 23L, 42L)
travel_jumps <- seq(from = 1887, to = 2052, by = 33)

anomaly <- travel_jumps - cursed_seq
print(anomaly)
```
The output shows the `anomaly`, or difference between the `travel_jumps` vector and the `cursed_seq` vector.

### 10.5 Task 5
Indexing named vectors
```{r 10.5 Task 5}
nerdy_palette <- c(
  "Octarine" = "#7F00FF",
  "TARDIS Blue" = "#003B6F",
  "Rebeccapurple" = "#663399",
  "Hooloovoo" = "#4F97A3",
  "Cosmic Latte" = "#FFF8E7",
  "Vantablack" = "#000000",
  "Matrix Green" = "#03A062",
  "Source Engine Magenta" = "#FF00FF",
  "Command Red" = "#CC0000",
  "Impossible Green" = "#4D9E68"
)

# nerdy_palette[c(7, 9)]
nerdy_palette[c("Matrix Green", "Command Red")]
```
Memo: First, I misread the instructions and indexed by the position, not the title. When I read Task 6 and realized that was in the next task, I returned to this task and changed nerdy_palette[c(7, 9)] to nerdy_palette[c("Matrix Green", "Command Red")] to retrieve the hex code using the color names.

### 10.6 Task 6
Indexing by position
```{r 10.6 Task 6}
nerdy_palette[c(2, 4, 6)]
```
Memo: This output is what I was expecting. Remember that vectors start indexing at "1", and not "0".

### 10.7 Task 7
Logical filtering + indexing practice
```{r 10.7 Task 7}
positive_growth <- growth[growth > 0]
last_two <- sales_q2[c(3, 4)]

print(positive_growth)
print(last_two)
```
The output shows that there were no values of positive growth between Q1 and Q2. It also shows that the last two values of `sales_q2` are 3 and 4.

Memo: This result was what I was expecting. Too bad there weren't any growth values greater than zero to illustrate `positive_growth`. Not a great quarter for business, hopefully Q3 sees an uptick in sales otherwise it is going to be a very rough year.

### 10.8 Task 8
Reflection: Numeric values may be coerced to character when mixed inside a single vector because characters are the most inclusive and flexible type, and therefore no values will become NA.

### 10.9 Task 9
Done!
